Paper Analysis

### 2024-07-10 Paper_WriteUp/Paper_Plots.qmd
adding some simple analyses that are used so that the qmd can reproduce all results in the paper

@@

@@

@@

bullet_data_gm |> 
  group_by(Username) |> 
  count() |> 
  arrange(n) |> 
  ungroup() |> 
  summarise(mean(n))

@@

ggsave(plot = hist_comp_global, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_comp_global.png")), dpi = 600,
       height = 5, width = 7)

@@

ggsave(plot = bul_blit_gm_comp_global, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_gm_global.png")), dpi = 600,
       height = 5, width = 7)

>>>>

lichess_data |> 
  mutate(Event = tolower(Event)) |> 
  filter(grepl("rated blitz game", Event)) |> 
  group_by(TimeControl) |> 
  count() |> 
  arrange(-n) |> 
  ungroup() |> 
  mutate(prop = n/sum(n))

@@

blitz_data <- lichess_data |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "180+0") %>%
  filter(Variant == "Standard") %>%
  filter(grepl("rated blitz game", Event))

@@

lichess_data_gm |> 
  mutate(Event = tolower(Event)) |> 
  filter(grepl("rated blitz game", Event)) |> 
  group_by(TimeControl) |> 
  count() |> 
  arrange(-n) |> 
  ungroup() |> 
  mutate(prop = n/sum(n))

@@

bullet_data_gm |> 
  group_by(Username) |> 
  count() |> 
  ungroup() |> 
  summarise(mean(n))

blitz_data_gm <- lichess_data_gm |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "180+0") %>%
  filter(Variant == "Standard") %>%
  filter(grepl("rated blitz game", Event))

blitz_data_gm |> 
  group_by(Username) |> 
  count() |> 
  ungroup() |> 
  summarise(mean(n))

## get the average rating of the GMs

lichess_data_gm |> 
  mutate(Event = tolower(Event)) |> 
  filter(grepl("rated blitz game", Event)) |> 
  group_by(Username) |> 
  arrange(UTCDate, UTCTime) |> 
  slice_tail(n = 1) |> 
  mutate(user_elo = ifelse(Username == White, WhiteElo, BlackElo)) |> 
  select(Username, White, Black, WhiteElo, BlackElo, user_elo) |>
  ungroup() |> 
  summarise(mean(user_elo))

@@

ggsave(plot = hist_comp_global, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_comp_global.png")), dpi = 600,
       height = 4, width = 7)

@@

ggsave(plot = bul_blit_gm_comp_global, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_gm_global.png")), dpi = 600,
       height = 4, width = 7)
